Supplemental material for `Eliminating object prior-bias from sparse-projection tomographic reconstructions'

### 2021-10-15 paper/post_tci_supplementary.tex
Minor edits in suppl material intro

\usepackage{boxedminipage}
%\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Supplemental material for `Eliminating object prior-bias from sparse-projection
tomographic reconstructions'}
\begin{document}
\date{}
\maketitle
This supplementary material consists of details which we did not
include in the main paper for purposes of brevity. This document
consists of links to view our complete 3D reconstructions, an
alternate simpler motivation for the use of multiple eigenspaces, and an
alternate method to compute the parameters for the weights map. We
also include a comparison with a method in literature based on
comments from a reviewer.

>>>>

\usepackage{boxedminipage}
%\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Supplemental material for `Eliminating object prior-bias from sparse-projection
tomographic reconstructions'}
\begin{document}
\date{}
\maketitle
This supplementary material consists of details which we did not
include in the main paper for purposes of brevity. This document
consists of links to view our complete 3D reconstructions, an
alternate simpler motivation for the use of multiple eigenspaces, and an
alternate learning-based method to compute weights map. %We
%also include a comparison with a method in literature based on
%comments from a reviewer.
